\documentclass[12pt]{article}

\usepackage[colorlinks=true]{hyperref}
\usepackage{xcolor}
\usepackage{natbib}
\usepackage[margin=1.5cm]{geometry}

\usepackage{tikz}

\usepackage[most]{tcolorbox}

\makeatletter
\newcommand*{\radiobutton}{%
  \@ifstar{\@radiobutton0}{\@radiobutton1}%
}
\newcommand*{\@radiobutton}[1]{%
  \begin{tikzpicture}
    \pgfmathsetlengthmacro\radius{height("X")/2}
    \draw[radius=\radius] circle;
    \ifcase#1 \fill[radius=.6*\radius] circle;\fi
  \end{tikzpicture}%
}
\makeatother

\usepackage{enumitem,amssymb}
\newlist{todolist}{itemize}{2}
\setlist[todolist]{label=$\square$}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\done}{\rlap{$\square$}{\raisebox{2pt}{\large\hspace{1pt}\cmark}}%
\hspace{-2.5pt}}
\newcommand{\wontfix}{\rlap{$\square$}{\large\hspace{1pt}\xmark}}

\title{Letter of Intent for \href{https://www.software.ac.uk/research-software-maintenance-fund/round-2}{Research Software Maintenance Fund -- Round 2}}
\author{}

\newenvironment{instruction}{%
    \begin{tcolorbox}[breakable,colback=red!5,colframe=red,title=Instruction]%
	}{%
    	\end{tcolorbox}%
	}

\begin{document}
\maketitle
\tableofcontents

\section{Start here}

\subsection{Category}

RSMF Round 2

\subsection{Application name}

Consolidating Bonsai as a Standard for Neuroscience Intelligent Experimental Control

\subsection{Research Area}

Biological, Medical and Veterinary Sciences

\pagebreak

\section{Elegibility}

\begin{instruction}

    This criterion considers whether the proposed work is in scope for and
    eligible for the Research Software Maintenance Fund (RSMF). The RSMF aims
    to fund work that will improve the sustainability of research software,
    particularly improving maintenance, reducing technical debt, improving user
    experience, and building community. The RSMF is especially interested in
    funding work for which it is hard to find funding elsewhere.

\end{instruction}

\subsection{Software to be maintained}

Bonsai

\subsection{Programming language}

C\#

\subsection{Software maturity and UK research benefit}

\begin{instruction}

    500 words

    Please demonstrate how the software(s) you maintain:

    \begin{itemize}

        \item Supports research being carried out in the United Kingdom.

        \item Is beyond the prototype/pilot stage and has had multiple stable /
            production releases (i.e. versions that have been released to end
            users, not just used for testing or evaluation).

        \item Is used by people outside their organisation(s) and is used
            beyond the immediate collaborators of the software’s
            developers/wider project team.

        \item Has mechanisms for raising issues, providing feedback, and adding
            additional contributors.

    \end{itemize}

\end{instruction}

\input{maturityAndUKresearchBenefit}

\subsection{Lead organization}

\begin{instruction}
    This is the legal organisation employing the Project Lead.

    The organisation needs to be \href{}{eligible for UKRI funding}.
\end{instruction}

\pagebreak

\section{Vision and impact}

\subsection{Motivation, Vision and Impact}

\begin{instruction}
    500 words

    \begin{itemize}

        \item The applicants demonstrate a clear need in the research community,
            a clear benefit to UK research, and the resulting impact on the
            research that is possible.

        \item The applicants understand the current software ecosystem (including
            other software used in this research area, and how this differs
            from their software) and researcher use cases / workflows (the way
            that software is used in combination) for the research areas their
            software targets.

        \item The vision of the proposed work is clearly articulated.

    \end{itemize}

\end{instruction}

\input{motivationVisionAndImpact}

\subsection{Benefits}

\begin{instruction}

    250 words

    \begin{itemize}

        \item The benefit to the long-term maintenance, governance, and
            adoption of the software is clearly demonstrated.

        \item The applicants demonstrate that the project will lead to
            advancement of good research software practices appropriate for
            their area / community.

        \item The project has considered how to increase the variety of users
            and contributors (for instance, the number of different
            organisations where users / contributors are based; the career
            stages of contributors).

    \end{itemize}

\end{instruction}

\input{benefitToUK}

\subsection{EDIA}

\begin{instruction}

    250 words

    \begin{itemize}

        \item The project has considered the accessibility of the software and
            explains how this could be improved

        \item The project understands their current position in relation to
            equity, diversity, and inclusivity and explains how this could be
            improved.

    \end{itemize}

\end{instruction}

\input{edia}

\pagebreak

\section{Feasibility and Approach}

\begin{instruction}

This criterion considers the way that the proposed work will be carried out.
Here we look for evidence that the funded work has a clear plan that will
deliver the objectives and benefits.

While we do not expect a budget at this stage of the application process,
please do keep in mind that the maximum we will fund is £150k for a duration of
one year.

\end{instruction}

\subsection{Proposed work}

\begin{instruction}

    500 words

    \begin{itemize}

        \item The objectives, activities and outputs of the work are clearly
            described and relate to each other and to the benefits.

        \item The project team have considered how the way they measure the
            progress of their project will be applied to this work.

    \end{itemize}

\end{instruction}

\input{proposedWork}

\subsection{Software sustainability}

\begin{instruction}

    250 words

    \begin{itemize}

        \item The future sustainability of the software (i.e. the software will
            continue to be available in the future, on new platforms, meeting
            new needs) has been considered, and the project has developed, or
            is committed to developing, a roadmap (a summary of the vision for
            the software and the direction of the software over time), a
            governance structure, and a sustainability/business plan.

    \end{itemize}

\end{instruction}

\input{sustainability}

\pagebreak

\section{Capability to Deliver}

\begin{instruction}

    This criterion considers the capability of the team, processes, and
    procedures in place for maintaining and developing software, and delivering
    the proposed work.

\end{instruction}

\subsection{Delivery team and mechanisms}

\begin{instruction}

    500 words

    \begin{itemize}

        \item The Leads / Co-Leads have appropriate skills, experience and
            connection to the software to achieve the objectives of the work.

        \item There are clear mechanisms for engaging the community and seeking
            external contributions and feedback, and how this will be
            incorporated into the work.

        \item Approaches to development of the software being used are suitable
            for the software and achieving the goals of the work.

    \end{itemize}

\end{instruction}

\input{deliveryTeamAndMechanisms}

\bibliographystyle{apalike}
\bibliography{bonsai}

\end{document}
